Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

>>>>

\section{Geometric Building Bricks} \label{sec:bricks}

This section will introduce four computational geometry problems, whose solutions will serve as building bricks for our $k$-SJ algorithm. Let us start with some terminology:
\myitems{
    \item For a horizontal segment $h = [x_1, x_2] \times y$ and a rectangle $r$, we call $r$ a {\em left-end covering rectangle} of $h$, if $r$ contains the left end point of $h$ (i.e., $(x_1, y) \in r$).
}

\begin{figure*}
    \begin{tabular}{cccc}
        \includegraphics[height=30mm]{./artwork/prob-a} &
        \includegraphics[height=30mm]{./artwork/prob-a} &
        \includegraphics[height=30mm]{./artwork/prob-a} &
        \includegraphics[height=30mm]{./artwork/prob-a}
    \end{tabular}

    \figcapup
    \caption{Four geometric building brick problems}
    \label{fig:probs}
    \figcapdown
\end{figure*}

\extraspacing {\bf Problem $\bm{\EuScript{A}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles, all in 2D space. The goal is to report, for each segment $h \in H$, the rightmost point $p$ on $h$ satisfying the condition that $p$ is covered by at least one left-end covering rectangle of $h$ in $R$ --- formally, for $h = [x_1, x_2] \times y$, we aim to find the maximum $x \in [x_1, x_2]$ such that some rectangle $r \in R$, which covers the left end point of $h$, contains the point $(x, y)$. If the point $p$ exists (equivalently, $h$ has at least one left-end covering rectangle in $R$), then we should output a tuple $(h, p)$; otherwise, we output nothing for $h$. In Figure~\ref{fig:probs}a
